---
title: |
  | Multitreat: Stata & Quarto^[Your acknowledgements. This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: |
  | **Your Name**^[Send correspondence to Your Name (\href{https://orcid.org/}{orcid.org/yourID}), Affiliation & School, Address, ZIP code & country.]
  | Affiliation & School
  | Your Email
date: |
  | `r loc <- Sys.getlocale(category = "LC_TIME"); Sys.setlocale("LC_TIME", "C"); fdate <- format(Sys.time(), '%B %e, %Y'); Sys.setlocale("LC_TIME", loc); fdate` \vspace{12cm}

format:
  pdf:
    documentclass: article
    number-sections: true
    colorlinks: true
    papersize: letter
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes

editor: visual

bibliography: references.bib
biblio-style: apsr

always_allow_html: yes

header-includes:
  - \usepackage[nolists]{endfloat}  
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{1em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \captionsetup[figure]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{svg}
  - \usepackage{amsmath}
  - \usepackage{blindtext}
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
if (!require(knitr)) {install.packages("knitr")}  
library(knitr)
opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
opts_chunk$set(out.width = '80%', dpi=600)
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache = FALSE)
```

\thispagestyle{empty}

\pagebreak

\setcounter{page}{1}

```{=tex}
\begin{center}
\vspace{2.5cm}
  \end{center}
```
```{=tex}
\begin{center}
\LARGE Multitreat: Stata \& Quarto
  \end{center}
\vspace{2cm}
```
```{=tex}
%\begin{abstract}
%\singlespace \blindtext
%    \end{abstract}
%\vspace{2cm}
```
```{=tex}
\begin{flushleft}
\textbf{Keywords}: Stata, Quarto, Reproducible Research, TWFE \newline
\textbf{Data Availability}: Sources identified in the text \newline
\textbf{Public Code Repository}: \href{https://github.com/trr266/treat}{github.com/trr266/treat}  \newline
\textbf{Declaration of Interest}: The authors declare that they have no conflict of interest \newline
  \end{flushleft}
```
\pagebreak

## Introduction

Hey there & congrats! You managed to skip the blindtext in the abstract. This means that we can dive into the world of reproducible research using coding languages like YAML, R, Stata, Python, Julia and many more... all from within one document: a **Quarto Markdown file (.qmd)**. Additionally, we provide you with two cherries on top of this futch: a template .qmd-file for your next paper in our public GitHub repository and & an exemplary application of one of the most common designs in causal research: a two way fixed effects research approach under recent considerations of @CS_2021. All set? Let's get started.

## Identification Strategy & Results

Writing a paper with Quarto Markdown allows you to switch between coding languages at your will. Easiest is the implementation of R and Python, but access to Stata works too. You can either import Stata output as .tex-files, e.g. by the courtesy of Stata's user written estout package or you immediately call Stata from within Quarto Markdown with the Statamarkdown package.[^1]

[^1]: \href{https://www.ssc.wisc.edu/\~hemken/Stataworkshops/Statamarkdown/stata-and-r-markdown.html}{www.ssc.wisc.edu/\~hemken/Stataworkshops/Statamarkdown/stata-and-r-markdown.html}

### Descriptive Statistics

```{r, warning=FALSE, echo=FALSE}
if (!require(devtools)) {install.packages("devtools")}  
library(devtools)
if (!require(devtools)) {install_github("hemken/Statamarkdown")}
```

```{r, echo = FALSE}
library(Statamarkdown)
```

```{stata, collectcode=TRUE, results="hide"}
use "../data/pulled/cstat_us_final.dta"
#
estpost tabstat y treated post, statistics(n mean sd min median max) columns(statistics)
#
esttab . using "../output/stata_descstats.tex", replace ///
  cells("Mean SD Min p50 Max") ///
  title("Descriptive Statistics") ///
  nonumbers nogaps ///
  coeflabels(y "\$\frac{sales}{lagged\,total\,assets}\$") ///
  addnotes("\label{tab:tbl-descstats}")
```

\input{../output/stata_descstats.tex}

This is some text that refers to Table \ref{tab:tbl-descstats}. 

### Difference-in-Differences with Multiple Time Periods

tbd @CS_2021

\input{../output/tbl_twfe.tex}

This is some text that refers to Table \ref{tab:tbl-twfe}. Let us now look at the results in Figure \ref{fig-twfe} or @fig-twfe

```{r fig-twfe, fig.cap = "ATT for 1008-treatment-short"}
if (!require(magick)) {install.packages("magick")}  
library(magick)
if (!require(rsvg)) {install.packages("rsvg")}  
library(rsvg)
magick::image_read_svg("../output/fig_twfe.svg", width=3000)
```

## Conclusion

\newpage

## References {.unnumbered}

\singlespacing

\small

::: {#refs}
:::

\doublespacing

\newpage

## Appendix {.unnumbered}

```{=tex}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{table}{0}
```
| Name | Definition | Source |
|------|------------|--------|
| VarA | tbd        | tbd    |
| VarB | tbd        | tbd    |
| VarB | tbd        | tbd    |

: Variable Definitions {#tbl-vars}

The .do-files for Stata comprise additional information to the explanations in @tbl-vars. Please refer to the Online Supplement.

\newpage

```{=tex}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}
```
\processdelayedfloats

\newpage

## Online Supplement {.unnumbered}

The public GitHub repository at \href{https://github.com/trr266/treat}{github.com/trr266/treat} contains .do-files for Stata (\*.do) and the Quarto markdown file (paper_stata.qmd).
