---
title: |
  | Multitreat: Stata & Quarto^[This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: |
  | **Your Name**^[Send correspondence to Your Name (\href{https://orcid.org/}{orcid.org/yourID}), Affiliation & School, Address, ZIP code & country.]
  | Affiliation & School
  | Your Email
date: |
  | `r loc <- Sys.getlocale(category = "LC_TIME"); Sys.setlocale("LC_TIME", "C"); fdate <- format(Sys.time(), '%B %e, %Y'); Sys.setlocale("LC_TIME", loc); fdate` \vspace{12cm}

format:
  pdf:
    documentclass: article
    number-sections: true
    colorlinks: true
    papersize: letter
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes

editor: visual

bibliography: references.bib
biblio-style: apsr

always_allow_html: yes

header-includes:
  - \usepackage[nolists]{endfloat}  
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{1em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \captionsetup[figure]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{svg}
  - \usepackage{amsmath}
  - \usepackage{blindtext}
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
if (!require(knitr)) {install.packages("knitr")}  
library(knitr)
opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
opts_chunk$set(out.width = '80%', dpi=600)
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache = FALSE)
#
#if (!require(RStata)) {install.packages("RStata")}  
#library(RStata)
#pathStata
#if(substr(path.expand("~"), 1, 1)=="C"){
#  pathStata <- readLines(paste0(file.path(dirname(path.expand("~")), "Desktop"), "/pathStata.txt"), warn = FALSE)
#} 
#options("RStata.StataPath" = paste0(pathStata))
#options("RStata.StataVersion" = 17)
```

\thispagestyle{empty}

\pagebreak

\setcounter{page}{1}

```{=tex}
\begin{center}
\vspace{2.5cm}
  \end{center}
```
```{=tex}
\begin{center}
\LARGE Multitreat: Stata \& Quarto
  \end{center}
\vspace{2cm}
```
```{=tex}
\begin{abstract}
\singlespace \blindtext
    \end{abstract}
\vspace{2cm}
```
```{=tex}
\begin{flushleft}
\textbf{Keywords}: Template, Stata, Quarto, Reproducible Research \newline
\textbf{Data Availability}: Sources identified in the text \newline
\textbf{Public Code Repository}: \href{https://github.com/trr266/treat}{github.com/trr266/treat}  \newline
\textbf{Declaration of Interest}: The authors declare that they have no conflict of interest \newline
  \end{flushleft}
```
\pagebreak

## Introduction

## Identification Strategy & Results

### Descriptive Statistics

tbd

```{r}
#stata_source <- ' 
#display "hello world"
#'
#stata(stata_source)
```

### Difference-in-Differences with Multiple Time Periods

tbd

\input{../output/tbl_twfe.tex}

This is some text that refers to Table \ref{tab:tbl-twfe}. Let us now look at the results in Figure \ref{fig:fig-twfe}

```{=tex}
\begin{figure}[p]
\centering
\caption{ATTs for 2008-treatment-cohort \label{fig:fig-twfe}}
\includegraphics[width=0.5\textwidth]{../output/fig_twfe.jpg}
\end{figure}
```
## Conclusion

\newpage

## References {.unnumbered}

\singlespacing

\small

::: {#refs}
:::

\doublespacing

\newpage

## Appendix {.unnumbered}

```{=tex}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{table}{0}
```
| Name | Definition | Source |
|------|------------|--------|
| VarA | tbd        | tbd    |
| VarB | tbd        | tbd    |
| VarB | tbd        | tbd    |

: Variable Definitions {#tbl-vars}

this is some text that refers to @tbl-vars

\newpage

```{=tex}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}
```
\processdelayedfloats

\newpage

## Online Supplement {.unnumbered}

The public GitHub repository at \href{https://github.com/trr266/treat}{github.com/trr266/treat} contains dofiles for Stata (\*.do) and the Quarto markdown file (paper_stata.qmd).
